mixchar

### 2018-08-08 README.Rmd
remove <hr> because not showing up properly in .md
remove print.process output

<hr>

@@

```{r}
tmp <- process(juncus, 
               init_mass = 18.96, 
               temp = 'temp_C', 
               mass_loss = 'mass_loss')
tmp
```

@@

# Acknowledgements
Thank you to Nick Tierney and David Wilkinson for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.

>>>>

@@

```{r}
tmp <- process(juncus, 
               init_mass = 18.96, 
               temp = 'temp_C', 
               mass_loss = 'mass_loss')
```

@@

# Acknowledgements

Thank you to Nick Tierney and David Wilkinson for valuable feedback during development. Thanks to the Holsworth Wildlife Reseach Endowment & The Ecological Society of Australia for support on this project.
